General purpose gene annotation using deep learning

### 2020-04-14 paper/main.tex
minor
class weights table

\begin{table}[!t]
\processtable{Class weights\label{tab:params_cw}} {
\begin{tabular}{@{}lll@{}}
\toprule Class & Animal Value & Plant Value \\
\midrule
[0.7, 1.6, 1.2, 1.2] & [0.3, 1.0, 0.9, 0.3] &\\
\botrule
\end{tabular}}{see data statistics tables..}
\end{table}

@@

\subsection{Overlapping evaluation by species}
\begin{figure}[!tpb]
\centerline{\includegraphics[height=0.01\paperheight]{images/overlapping/animals_overlapping}}
\caption{Caption, caption.}\label{fig:animals_overlapping}
\end{figure}

>>>>

\begin{table}[!t]
\processtable{Class weights\label{tab:params_cw}} {
\begin{tabular}{@{}lll@{}}
\toprule Class & Animal Value & Plant Value \\
\midrule
	Intergenic & 0.7 & 0.3 \\
	UTR & 1.6 & 1.0 \\
	CDS & 1.2 & 0.9 \\
	Intron & 1.2 & 0.3 \\
\botrule
\end{tabular}}{The class weights are the only hyperparameters that are different for animals and plants. The exact weights were determined manually and partially reflect the difference in the class distributions of both datasets (see Table \ref{tab:statistics_all}). All other hyperparameters are shown in Table \ref{tab:params}.}
\end{table}

@@

\subsection{Overlapping evaluation by species}
\begin{figure}[!tpb]
% \centerline{\includegraphics[height=0.01\paperheight]{images/overlapping/animals_overlapping}}
\caption{Caption, caption.}\label{fig:animals_overlapping}
\end{figure}
